---
title: "Problem Set One"
author: "Christine Schulz"
date: "January 22, 2022"
output: 
  pdf_document:
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Load in the gss_panel.RData file
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(fixest)
library(sjPlot)


load("~/R/gss_panel.RData")
```
# 2. Construct three visualizations that are aesthetically well formatted (axis labels, formatting, etc.)
## Visualization 1: Raw correlations
```{r, warning=FALSE, message=FALSE}
gss_panel %>% 
  filter(!is.na(natenviy)) %>% 
  mutate(repub = as.factor(ifelse(as.factor(partyid)%in% 
                                    c("4", "5", "6"), 1, 0)),
         natenviy = factor(natenviy, labels = 
                             c("Too little", "About right", 
                               "Too much"))) %>% 
  ggplot(aes(x = natenviy, color = repub, fill = repub)) +
  geom_bar(position = "dodge")+
  scale_color_manual(name = "Party",
                     labels = c("Democrat", "Republican"), 
                     values = c("blue", "red")) +
  scale_fill_manual(name = "Party",
                     labels = c("Democrat", "Republican"), 
                     values = c("blue", "red")) +
  labs(title = "Spending on the Environment 
       by Political Political Party", 
       x = "Environmental Spending",
       y = "Count") +
  theme_bw() 
```
## Visualization 2: Some sort of group-based visualization (ignoring time structure)
```{r, warning=FALSE, message=FALSE}
gss_panel$repub <- ifelse(as.factor(gss_panel$partyid)%in% 
                            c("4", "5", "6"), 1, 0)
gss_panel %>%
  filter(!is.na(natenviy)) %>% 
  mutate(natenviy = as.factor(natenviy),
         repub = factor(repub, labels = 
                          c("Democrat", "Republican"))) %>% 
  ggplot(aes(x = age, color = natenviy, fill = natenviy, group = natenviy))+
  geom_density(alpha = .4) +
  facet_wrap(~ repub) +
  scale_color_manual(name = "Environmental Spending",
                     labels = c("Too little", "About right", "Too much"), 
                     values = c("red", "green", "blue")) +
  scale_fill_manual(name = "Environmental Spending",
                    labels = c("Too little", "About right", "Too much"),
                      values = c("red", "green", "blue")) +
  labs(title = "Opinions on Environmental Spending by Age and Party",
       x = "Age",
       y = "Density") +
  theme_bw()

```
## Visualization 3: A group and time-based visualization
```{r, warning=FALSE, message=FALSE}
gss_panel %>%
  filter(!is.na(natenviy)) %>% 
  mutate(natenviy = as.factor(natenviy),
         repub = factor(repub, labels = c("Democrat", "Republican"))) %>% 
  ggplot(aes(x = age, color = natenviy, fill = natenviy, group = natenviy))+
  geom_density(alpha = .4) +
  facet_wrap(~ year + repub) +
  scale_color_manual(name = "Spending on the Environment",
                     labels = c("Too little", "About right", "Too much"), 
                     values = c("red", "green", "blue")) +
  scale_fill_manual(name = "Spending on the Environment",
                    labels = c("Too little", "About right", "Too much"),
                      values = c("red", "green", "blue")) +
  labs(title = "Opinions on Environmental Spending by Age, Party, and Year",
       x = "Age",
       y = "Density") +
  theme_bw() 
```

# 3. Run two OLS models, including relevant controls -- and discuss WHY the controls are relevant. 
# (Remember, you have a lot of flexibility here, including but not limited to interactions, fixed effects, recoding variables, etc.)
## Model 1: Ignoring time element

```{r, warning=FALSE, message=FALSE}
gss_panel <- gss_panel %>% 
  mutate(educ = as.factor(educ),
         relig = factor(relig, labels = 
                          c("Protestant", "Catholic", "Jewish",
                            "None", "Other", "Buddhism", "Hinduism", 
                            "Other Eastern Religions", "Muslim/Islam", 
                            "Orthodox Christian", "Christian", 
                            "Native American", "Inter-nondenominational")),
         coninc = log(coninc),
         natenviy = ifelse(natenviy == 2 | natenviy == 3, 0, 1))
table(gss_panel$natenviy)


m1 <- lm(natenviy ~ repub + age + repub:age, gss_panel)

```

## Model 2: Taking into account time element

```{r, warning=FALSE, message=FALSE}
m2 <- feols(natenviy ~ repub + age + relig + educ + coninc | year, se = "hetero", gss_panel)
```

# 4. Create an interesting and informative visualization using either coefficients from model 1 or 2 or predicted values from model 1 or 2.
## Discuss why you think this visualization tells us something that wasn't necessarily obvious by just interpreting the model results.
```{r, warning=FALSE, message=FALSE}
plot_model(m1, type = "pred", terms = c("age", "repub"), 
           title = "Predicted Values of Environmental Spending",
           axis.title = c("Age", "Environmental Spending")) +
  scale_color_manual(name = "Party",
                     labels = c("Democrat", "Republican"), 
                     values = c("blue", "red")) +
  scale_fill_manual(name = "Party",
                    labels = c("Democrat", "Republican"),
                    values = c("blue", "red"))+
  theme_bw() 
```